---
title: "Chapter4: Latitude - Growth Data"
author: "Elliott Schmidt"
date: "`r Sys.Date()`"
output: 
  html_document: 
    toc: true  
    toc_depth: 6 
    toc_float: true
    df_print: paged
---
# Scenario 

Within this chapter developmental plasticity was explored within _Acanthochromis polyacanthus_ that were collected from two different regions (i.e., low-latitude, Cairns, and high-latitude, Mackay). Fish were held in common garden experiments at 28.5 C. Clutch data was collected along with parental morphometeric data to determine how fish from each population performed at 28.5 C, a temperature that was shown to produce similar absoluate aerobic scope performances in a previous study [link]. Once hatched offspring were placed into three different temperature treatments, 28.5, 30, and 31.5 C. After approximately 5-6 months offspring length and weight was measured, as well as CTmax and respiration during CTmax trials. 

# Load packages 

```{r load packages, warning=FALSE, message=FALSE}
library(tidyverse) # data manipulation

```

# Set working directory 

```{r setwd, echo=FALSE}
knitr::opts_knit$set(root.dir=""C:/Users/jc527762/OneDrive - James Cook University/PhD dissertation/Data/Chapter4_Latitude"")
``` 

```{r setwd-2, echo=TRUE, eval=FALSE}
knitr::opts_knit$set(root.dir=working.dir)
```

# Import data 

```{r import-data}
growth <- read_delim("import_files/growth_data.txt", 
    delim = "\t", escape_double = FALSE, 
    col_types = cols(NOTES = col_skip(), 
        ...16 = col_skip(), ...17 = col_skip()), 
    trim_ws = TRUE) 

clutch_data <- read_delim("import_files/clutch_data_2022_2023.txt", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE) %>% 
  mutate(CLUTCH_NUMBER = as.factor(CLUTCH_NUMBER))
```

# Data manipulation 

```{r data-manipulation, warning=FALSE}
growth2 <- growth |> 
  mutate(CLUTCH_NUMBER = as.factor(CLUTCH_NUMBER), 
         MALE = as.factor(MALE), 
         FEMALE = as.factor(FEMALE), 
         REGION = as.factor(REGION), 
         POPULATION = as.factor(POPULATION), 
         DATE_OF_HATCH = as.Date(DATE_OF_HATCH, format = "%d/%m/%Y"), 
         DATE_SAMPLED = as.Date(DATE_SAMPLED, format = "%d/%m/%Y"), 
         DEV_TEMP = as.factor(DEV_TEMP), 
         TANK = as.factor(TANK), 
         REP = as.factor(REP), 
         LENGTH = as.numeric(LENGTH), 
         MASS = as.numeric(MASS), 
         FULTONK = (1000*MASS)/(LENGTH^3), # Adding FULTON'S K metric
         EXPERIMENT = as.factor(EXPERIMENT)) |> 
  full_join(select(clutch_data, c("CLUTCH_NUMBER",
                                   "MALE_STANDARD_LENGTH", 
                                   "MALE_MASS", 
                                   "MALE_LAT", 
                                   "MALE_LONG", 
                                   "FEMALE_STANDARD_LENGTH", 
                                   "FEMALE_MASS", 
                                   "FEMALE_LAT", 
                                   "FEMALE_LONG", 
                                   "CLUTCH_ORDER", 
                                   "DAYS_IN_TREATMENT", 
                                   "EGG_COUNT", 
                                   "HATCHING_SUCCESS")), by = "CLUTCH_NUMBER") |> 
  select(c(1:6,16:27,7:13,15,14)) |> 
  mutate(CLUTCH_ORDER = as.factor(CLUTCH_ORDER))
```