---
title: "03.CTmax_analysis"
author: "Elliott Schmidt"
date: "`r Sys.Date()`"
output: 
  html_document: 
    toc: true  
    toc_depth: 2
    toc_float: true
    code_folding: show
    collapse: no
    df_print: paged
    fig_caption: yes
    fig_height: 4
    fig_width: 6
    highlight: monochrome
    theme: cerulean
    latex_engine: xelatex
---

# Scenario 

Within this chapter developmental plasticity was explored within _Acanthochromis polyacanthus_ that were collected from two different regions (i.e., low-latitude, Cairns, and high-latitude, Mackay). Fish were held in common garden experiments at 28.5 C. Clutch data was collected along with parental morphometeric data to determine how fish from each population performed at 28.5 C, a temperature that was shown to produce similar absoluate aerobic scope performances in a previous study [link]. Once hatched offspring were placed into three different temperature treatments, 28.5, 30, and 31.5 C. After approximately 5-6 months offspring length and weight was measured, as well as CTmax and respiration during CTmax trials. 

# Load packages 

```{r load-packages-1, warning=FALSE, message=FALSE}
library(tidyverse) # data manipulation
library(ggpubr) # figure arrangement 
library(brms) # Bayesian models
library(StanHeaders)# needed to run Bayesian models
library(rstan) # needed to run Bayesian models
library(standist) # needs to be installed 
library(bayesplot) # needed for MCMC diagnostics 
library(DHARMa) # model validation 
library(ggdist) # partial plots 
library(tidybayes) # partial plots 
library(broom.mixed) # model investigation
library(emmeans) # pairwise comparisons
library(rstanarm) # pairwise comparisons - need for emmeans
```

# Set working directory 

```{r setwd-1, echo=FALSE}
knitr::opts_knit$set(root.dir="C:/Users/jc527762/OneDrive - James Cook University/PhD dissertation/Data/Chapter4_Latitude")
``` 

```{r setwd-2, echo=TRUE, eval=FALSE}
knitr::opts_knit$set(root.dir=working.dir)
```

# Import data 

```{r import-data-1, message=FALSE}
growth <- read_delim("import_files/growth_data.txt", 
    delim = "\t", escape_double = FALSE, 
    col_types = cols(NOTES = col_skip(), 
        ...16 = col_skip(), ...17 = col_skip()), 
    trim_ws = TRUE) 

clutch_data <- read_delim("import_files/clutch_data_2022_2023.txt", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE) %>% 
  mutate(CLUTCH_NUMBER = as.factor(CLUTCH_NUMBER))
```
