---
title: "05. Egg counts"
author: "Elliott Schmidt"
date: "`r Sys.Date()`"
output: 
  html_document: 
    toc: true  
    toc_depth: 4
    toc_float: true
    code_folding: show
    collapse: no
    df_print: paged
    fig_caption: yes
    fig_height: 4
    fig_width: 6
    highlight: monochrome
    theme: cerulean
    latex_engine: xelatex
--- 

# Scenario 

Within this chapter developmental plasticity was explored within _Acanthochromis polyacanthus_ that were collected from two different regions (i.e., low-latitude, Cairns, and high-latitude, Mackay). Fish were held in common garden experiments at 28.5 C. Reproductive meterics are only relevant to parental fish. Understanding potential differences in reproduction within fish from low- and high-latitude populations will provide basis of where juveniles are starting from. 

# Load packages 

```{r load-packages-1, warning=FALSE, message=FALSE}
library(tidyverse) # data manipulation
library(ggpubr) # figure arrangement 
library(brms) # Bayesian models
library(StanHeaders)# needed to run Bayesian models
library(rstan) # needed to run Bayesian models
library(standist) # needs to be installed 
library(bayesplot) # needed for MCMC diagnostics 
library(DHARMa) # model validation 
library(ggdist) # partial plots 
library(tidybayes) # partial plots 
library(broom.mixed) # model investigation
library(emmeans) # pairwise comparisons
library(rstanarm) # pairwise comparisons - need for emmeans
library(car)
```


# Set working directory 

```{r setwd-1, echo=FALSE}
knitr::opts_knit$set(root.dir="C:/Users/jc527762/OneDrive - James Cook University/PhD dissertation/Data/Chapter4_Latitude")
``` 

```{r setwd-2, echo=TRUE, eval=FALSE}
knitr::opts_knit$set(root.dir=working.dir)
```

# Import data 

Note that when making the datasheet, each clutch was designated an 'experimental_number' that is associated with which experiment(s) clutches were involved in, therefore when importing the data, we will filter data to give us only clutches that were used in the relevent 'developmental plasticity experiment'. We are also dropping one clutch that was found only when individuals hatched, meaning we don't know the clutch size, or hatching success

```{r import-data-1, message=FALSE}
clutch_data <- read_delim("import_files/clutch_data_2022_2023.txt", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE) |> 
  mutate(PROJECT_CODE = factor(PROJECT_CODE)) |>
  filter(PROJECT_CODE == "2"| 
         PROJECT_CODE == "3"|
         PROJECT_CODE == "6"|
         PROJECT_CODE == "7") |> 
  drop_na(EGG_COUNT)
```  

We are left with 20 clutches; 12 from the Core region (from 11 unique pairs), and 8 from the leading region (from 5 unique pairs). 

# Data manipulation 

```{r data-manipulation, warning=FALSE}
clutch_data2 <- clutch_data |> 
  mutate(CLUTCH_NUMBER = as.factor(CLUTCH_NUMBER), 
         MALE = factor(MALE), 
         FEMALE = factor(FEMALE), 
         REGION = factor(REGION), 
         POPULATION = factor(POPULATION),
         CLUTCH_ORDER = factor(CLUTCH_ORDER),
         DATE_OF_HATCH = as.Date(DATE_OF_HATCH, format = "%d/%m/%Y"), 
         cMALE_MASS = scale(MALE_MASS, center=TRUE, scale=FALSE), 
         cFEMALE_MASS = scale(FEMALE_MASS, center=TRUE, scale=FALSE), 
         cEGG_COUNT = scale(EGG_COUNT, center=TRUE, scale=FALSE),
         FEMALE_MASS = coalesce(FEMALE_MASS, MALE_MASS))
``` 

# Exploratory data analysis 

## Egg counts 

```{r eda-1, warning=FALSE, message=FALSE, echo=FALSE}
ggplot(clutch_data2, aes(x=REGION, y=EGG_COUNT, fill=REGION)) + 
  geom_boxplot() + 
  scale_y_continuous(limits = c(0, 800), breaks = seq(0,800, 100)) +
  theme_classic()

ggplot(clutch_data2, aes(x=MALE_MASS, y=EGG_COUNT, color=REGION)) + 
  geom_point() + 
  scale_y_continuous(limits = c(0, 800), breaks = seq(0,800, 100)) + 
  geom_smooth(method = "lm") +
  theme_classic()
```


# Fit model [random factors] 

Two different hypotheses will be tested to determine which fixed factors will make it into our final model. The first mode will look at fixed factors that are essential to the question being asked, the second tested hypothesis will see if temporal factors such as clutch order and days in treatment influence the outcome. 

MALE_MASS and FEMALE_MASS are correlated and therefore only one is included within the model. FEMALE_MASS was included as it may be more influential when dealing with reproductive metrics. One Female did not have mass data collected due to a mortality event that would have made MASS data unreliable. For this female the male weight was used, because the both individuals were ~the same LENGTH, and LENGTH and MASS are highly correlated. 

Hypothesis test will include: 

0. Null model  
1. EGG_COUNT ~ 1 + (1| FEMALE)
2. EGG_COUNT ~ 1 + (1| FEMALE) + (1| POPULATION)  
3. EGG_COUNT ~ 1 + (1| FEMALE) + (1| CLUTCH_ORDER) 
4. EGG_COUNT ~ 1 + (1| FEMALE) + (1| POPULATION) + (1| CLUTCH_ORDER)

# Priors 

```{r prior-investigation}
clutch_data2 |> 
  group_by(REGION) |> 
  summarise(mean(na.omit(EGG_COUNT)), 
            sd(na.omit(EGG_COUNT))) 

eggcount.priors <- prior(normal(425, 100), class="Intercept") 
```

## Models {.tabset}

### Null 

```{r formula-null}
f.null <- bf(EGG_COUNT ~ 1, 
                     family=poisson())



```

```{r null, cache=TRUE}
model.null <- brm(f.null,
              data = clutch_data2, 
              prior = eggcount.priors,
              warmup = 500, 
              iter = 5000,
              seed=123, 
              cores=2, 
              save_pars = save_pars(all=TRUE), 
              sample_prior = "yes",
              chains = 2, 
              thin = 5, 
              control = list(adapt_delta=0.95)) 
 
saveRDS(model.null, file="./05.Reproductive_metrics_files/model_null_eggcount.RDS")
```

### Model1 

```{r f.model1}
f.model1 <- bf(EGG_COUNT ~ 1 + (1| FEMALE), 
                     family=poisson())

```

```{r model1, cache=TRUE}
model1 <- brm(f.model1,
              data = clutch_data2, 
              prior = eggcount.priors,
              warmup = 500, 
              iter = 5000,
              seed=123, 
              cores=2, 
              save_pars = save_pars(all=TRUE), 
              sample_prior = "yes",
              chains = 2, 
              thin = 5, 
              control = list(adapt_delta=0.95)) 
 
saveRDS(model1 , file="./05.Reproductive_metrics_files/model1_eggcount.RDS")
```

### Model2


```{r f.model2}
f.model2 <- bf(EGG_COUNT ~ 1 + (1| FEMALE) + (1| POPULATION) , 
                     family=poisson())

```

```{r fit-model-1, cache=TRUE}
model2 <- brm(f.model2,
              data = clutch_data2, 
              prior = eggcount.priors,
              warmup = 500, 
              iter = 5000,
              seed=123, 
              cores=2, 
              save_pars = save_pars(all=TRUE), 
              sample_prior = "yes",
              chains = 2, 
              thin = 5, 
              control = list(adapt_delta=0.95)) 

saveRDS(model2 , file="./05.Reproductive_metrics_files/model2_eggcount.RDS")
```

### Model 3 


```{r f.model3}
f.model3 <- bf(EGG_COUNT ~ 1 + (1| FEMALE) + (1|CLUTCH_ORDER), 
                     family=poisson())

```

```{r fit-model-3, cache=TRUE}
model3 <- brm(f.model3,
              data = clutch_data2, 
              prior = eggcount.priors,
              warmup = 500, 
              iter = 5000,
              seed=123, 
              cores=2, 
              save_pars = save_pars(all=TRUE), 
              sample_prior = "yes",
              chains = 2, 
              thin = 5, 
              control = list(adapt_delta=0.95)) 

saveRDS(model3 , file="./05.Reproductive_metrics_files/model3_eggcount.RDS")
```

### Model 4 


```{r f.model4}
f.model4 <- bf(EGG_COUNT ~ 1 + (1| FEMALE) + (1|POPULATION) + (1|CLUTCH_ORDER), 
                     family=poisson())

```

```{r fit-model-4, cache=TRUE}
model4 <- brm(f.model4,
              data = clutch_data2, 
              prior = eggcount.priors,
              warmup = 500, 
              iter = 5000,
              seed=123, 
              cores=2, 
              save_pars = save_pars(all=TRUE), 
              sample_prior = "yes",
              chains = 2, 
              thin = 5, 
              control = list(adapt_delta=0.95)) 

saveRDS(model4 , file="./05.Reproductive_metrics_files/model4_eggcount.RDS")
```

### {-}

## LOO
```{r model-comparisons-re}
LOO(model.null, model1, model2, model3, model4) 
```

The model with clutch order scores the best here, but does not perform well in models below. Random factors used below will contain the random factor(s) in **model2.eggcount.re**.

# Fit model [fixed factors] {.tabset}

Before testing models a quick analysis of collinearity will be tested due to the likely hood of CLUTCH_ORDER and DAYS_IN_TREATMENT being correlated to each other

```{r collinearity}
mcol <- lm(EGG_COUNT ~ 1 + 
                       REGION + CLUTCH_ORDER + 
                       scale(DAYS_IN_TREATMENT, center=TRUE, scale=TRUE) +
                       scale(MALE_MASS, center=TRUE, scale=TRUE), 
           family=gaussian(),  
           data=clutch_data2); vif(mcol) 

```

As a result CLUTCH_ORDER will be removed from the model


Two different hypotheses will be tested: 

1. EGG_COUNT ~ 1 + REGION + scale(FEMALE_MASS, center=TRUE, scale=TRUE) + scale(DAYS_IN_TREATMENT, center=TRUE, scale=TRUE) + 
   (1| FEMALE) + (1|POPULATION) + (1|CLUTCH_ORDER)
   
2. EGG_COUNT ~ 1 + REGION * scale(FEMALE_MASS, center=TRUE, scale=TRUE) + scale(DAYS_IN_TREATMENT, center=TRUE, scale=TRUE) + 
   (1| FEMALE) + (1|POPULATION) + (1|CLUTCH_ORDER) 

** Notice the interaction term in the second model

## Priors {.tabset}
```{r Priors-classb}
clutch_data2 |> 
  group_by(REGION) |> 
  summarise(mean(na.omit(EGG_COUNT)), 
            sd(na.omit(EGG_COUNT))) 

eggcount.priors <- prior(normal(425, 100), class="Intercept") +  
  prior(normal(0, 40), class="b")
```

### Model1.1
```{r model1.1}
f.model1.1 <- bf(EGG_COUNT ~ 1 + REGION + 
                       scale(FEMALE_MASS, center=TRUE, scale=TRUE) +
                       scale(DAYS_IN_TREATMENT, center=TRUE, scale=TRUE) +
                       (1| FEMALE) + (1|POPULATION) + (1|CLUTCH_ORDER), 
                       family=poisson())
```

```{r fit-model1.1, cache=TRUE}
model1.1 <- brm(f.model1.1,
              data = clutch_data2, 
              prior = eggcount.priors,
              warmup = 500, 
              iter = 5000,
              seed=123, 
              cores=2, 
              save_pars = save_pars(all=TRUE),  
              sample_prior = "yes",
              chains = 2, 
              thin = 5, 
              control = list(adapt_delta=0.99))
saveRDS(model1.1, file="./05.Reproductive_metrics_files/model1.1_eggcount.RDS")
```
### Model 1.2

```{r priors-fixed2}
f.model1.2 <- bf(EGG_COUNT ~ 1 + REGION*scale(MALE_MASS, center=TRUE, scale=TRUE) + 
                       scale(DAYS_IN_TREATMENT, center=TRUE, scale=TRUE) +
                       (1| FEMALE) + (1|POPULATION) + (1|CLUTCH_ORDER), 
                     family=poisson())
```

```{r fit-model2.eggcount, cache=TRUE}
model1.2 <- brm(f.model1.2,
              data = clutch_data2, 
              prior = eggcount.priors,
              warmup = 500, 
              iter = 5000,
              seed=123, 
              cores=2, 
              save_pars = save_pars(all=TRUE),  
              sample_prior = "yes",
              chains = 2, 
              thin = 5, 
              control = list(adapt_delta=0.99))
saveRDS(model1.2, file="./05.Reproductive_metrics_files/model1.2_eggcount.RDS")
```

### {-}

# LOO
```{r model-comparisons-2}
LOO(model1.1, model1.2) 
#reloo=TRUE) 
#moment_match = TRUE
```

# Model performance
```{r fit-model2-diag, fig.height=9}
stan_trace(model1.1$fit)
stan_ac(model1.1$fit) 
stan_rhat(model1.1$fit) 
stan_ess(model1.1$fit)
stan_dens(model1.1$fit, separate_chains = TRUE)
```

# Model diagnositics 

```{r diag-1}
#--- distribution check ---#
pp_check(model1.1, type = 'dens_overlay_grouped', ndraws=150, group="REGION")
```

```{r diag-2}
preds <- posterior_predict(model1.1, ndraws=250, summary=FALSE)
model1.1_resids <- createDHARMa(simulatedResponse = t(preds), 
                              observedResponse = na.omit(clutch_data2$EGG_COUNT), 
                              fittedPredictedResponse = apply(preds, 2, mean), 
                              integerResponse = 'student')
plot(model1.1_resids) ; testDispersion(model1.1_resids)
``` 

# Partial effects plots 

```{r partial-plots-cond-eff-1}
model1.1 |> 
  conditional_effects(spaghetti = TRUE, ndraws=200)
``` 

# Model investigation {.tabset}

## summary 

```{r summary-100}
summary(model1.1)
```

## R2 

```{r r-squared}
model1.1 |> bayes_R2(summary = FALSE) |> median_hdci()
```

## tidyMCMC 

```{r tidy}
tidyMCMC(model1.1, estimate.method='median', conf.int=TRUE, conf.method='HPDinterval')
```

## gather draws 

```{r gather_draws}
#model1.re.wo |> get_variables()
model1.1 |> gather_draws(`b_.*|sigma`, regex =TRUE) |> 
  median_hdci()
``` 

## bayesplot 

```{r bayesplot-1}
model1.1 |> mcmc_plot(type='intervals')
```

## emmeans - pariwise 

```{r emmeans-pairwise}
model1.1 |> emmeans(pairwise ~ REGION, type="response") |> summary()
```

## probabilities 
```{r probabilities}
#model2.eggcount |> emmeans(~ REGION | DEV_TEMP, at = list(DEV_TEMP = 31.5, length.out = 10)) |> pairs(type = 'response')
mtsqst <- model1.1 |> emmeans(pairwise ~ REGION)
mtsqrt1 <- mtsqst$contrasts |> gather_emmeans_draws()
mtsqrt1 %>% group_by(contrast) %>% dplyr::summarise(Prob = sum(.value>0)/n())
```

## {-}

# summary figure 

```{r summary-figure-1, warning=FALSE, message=FALSE}
var <- get_variables(model1.1)
var1 <- get_variables(model1.1)[c(1:2)] 

int_draws_spread <- model1.1 |> spread_draws(!!!syms(var1)) 

int_draws_spread2 <- int_draws_spread |> 
  gather_draws(b_Intercept, b_REGIONleading) |> 
  left_join(int_draws_spread, by = c(".chain",".iteration",".draw"))


int_draws <- int_draws_spread2 |> 
  mutate(RCore = case_when(`.variable` == 'b_Intercept' ~ 
                             `.value`, 
                           `.variable` != 'b_Intercept' ~ 
                             `.value` + b_Intercept), 
         
         RLeading = case_when(`.variable` == 'b_Intercept' ~ 
                           `.value` + b_REGIONleading, 
                         `.variable` == 'b_REGIONleading' ~ 
                           `.value` + b_Intercept + `b_REGIONleading`))

int_draws_plotting <- int_draws |> 
  pivot_longer(cols = starts_with("R"), 
               names_to = "REGION", 
               values_to = "EGG_COUNT") |> 
  transmute(LATITUDE = case_when(`.variable` == "b_Intercept" ~ "Low latitude", 
                                 `.variable` == "b_REGIONleading" ~ "High latitude"),
            EGG_COUNT = EGG_COUNT, 
            LATITUDE_B = LATITUDE,
            chain = `.chain`, 
            iteration = `.iteration`, 
            draw_n = `.draw`) |> 
  mutate(rEGG_COUNT = exp(EGG_COUNT))

eggcount.plot <- int_draws_plotting |> 
  ggplot(aes(x=LATITUDE, y=rEGG_COUNT)) + 
  #geom_hline(yintercept = 0, linetype="dashed", linewidth=1, color="grey58", alpha=0.8) + 
  stat_halfeye(aes(fill = LATITUDE, fill_ramp = after_stat(level)), 
               point_interval = mode_hdci, 
               .width = c(.66, .90, .95)) + 
  scale_fill_ramp_discrete(na.translate=FALSE, 
                           labels =c("0.95","0.90","0.66"), 
                           name = "Credible interval") +
  scale_fill_manual(values = c("lightskyblue","coral"))+ 
  #scale_y_continuous(limits=c(0,2), breaks = seq(0,2, .5))+
  ylab("EGG COUNT") + xlab("EXPERIMENTAL GROUP") +
  scale_x_discrete(labels = c("Low latitude" = paste0("Low latitude"), 
                              "High latitude" = paste0("High latitude"))) +
  #annotate("text", x=6.8,y=1.4, label = paste0(round(mean(growth3$MASS), 2)," (mm)"), color="grey58") +
  coord_flip() + 
  theme_classic() + 
  guides(fill = "none") + 
  theme(legend.position = c(.15,.86), 
        axis.title.y = element_text(margin = margin(r =0.3, unit = "in"), size = 12), 
        axis.title.x = element_text(margin = margin(t = 0.3, unit="in"), size =12), 
        legend.key = element_rect(color="black", size=1.25), 
        legend.background = element_rect(fill = alpha("blue", 0))); eggcount.plot 

ggplot(clutch_data2, aes(FEMALE_MASS))+ 
  geom_dotplot() + 
  geom_density() +
  facet_wrap(~REGION) + 
  ylim(0,0.15) + 
  ggtitle("FEMALE MASS")
```


















