---
title: "09.Reproductive_output"
author: "Elliott Schmidt"
date: "`r Sys.Date()`"
output: 
  html_document: 
    toc: true  
    toc_depth: 2
    toc_float: true
    code_folding: show
    collapse: no
    df_print: paged
    fig_caption: yes
    fig_height: 4
    fig_width: 6
    highlight: monochrome
    theme: cerulean
    latex_engine: xelatex
---

# Scenario 

Within this chapter developmental plasticity was explored within Acanthochromis polyacanthus that were collected from two different regions (i.e., low-latitude, Cairns, and high-latitude, Mackay). Fish were held in common garden experiments at 28.5 C. Reproductive meterics are only relevant to parental fish. Understanding potential differences in reproduction within fish from low- and high-latitude populations will provide basis of where juveniles are starting from.

# Load packages

```{r load-packages, warning=FALSE, message=FALSE}
library(car)
library(tidyverse) # data manipulation
library(ggpubr) # figure arrangement 
library(brms) # Bayesian models
library(StanHeaders)# needed to run Bayesian models
library(rstan) # needed to run Bayesian models
library(standist) # needs to be installed 
library(bayesplot) # needed for MCMC diagnostics 
library(DHARMa) # model validation 
library(ggdist) # partial plots 
library(tidybayes) # partial plots 
library(broom.mixed) # model investigation
library(emmeans) # pairwise comparisons
library(rstanarm) # pairwise comparisons - need for emmeans
library(effectsize)
```

# Set working directory 

```{r setwd-1, echo=FALSE}
knitr::opts_knit$set(root.dir="C:/Users/jc527762/OneDrive - James Cook University/PhD dissertation/Data/Chapter4_Latitude")
``` 

```{r setwd-2, echo=TRUE, eval=FALSE}
knitr::opts_knit$set(root.dir=working.dir)
``` 

# Import data 

Note that when making the datasheet, each clutch was designated an 'experimental_number' that is associated with which experiment(s) clutches were involved in, therefore when importing the data, we will filter data to give us only clutches that were used in the relevant 'developmental plasticity experiment'. We are also dropping one clutch that was found only when individuals hatched, meaning we don't know the clutch size, or hatching success.

```{r Import-data}
egg_size <- read_delim("import_files/egg_size_data_2022_2023.txt", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)

clutch_data <- read_delim("import_files/clutch_data_2022_2023.txt", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE) |> 
  mutate(PROJECT_CODE = factor(PROJECT_CODE)) |>
  filter(PROJECT_CODE == "2"| 
         PROJECT_CODE == "3"|
         PROJECT_CODE == "6"|
         PROJECT_CODE == "7") |> 
  drop_na(EGG_COUNT)
```

# Data manipulation 
```{r data-manipulation}
egg_size2 <- egg_size |> 
  mutate(CLUTCH_NUMBER = as.factor(CLUTCH_NUMBER), 
         MALE = factor(MALE), 
         FEMALE = factor(FEMALE), 
         REGION = factor(REGION), 
         POPULATION = factor(POPULATION),
         CLUTCH_ORDER = factor(CLUTCH_ORDER),
         DATA_EGGS_FOUND = as.Date(DATA_EGGS_FOUND, format = "%d/%m/%Y")) |> 
  select(-c("NOTES","...18")) |> 
  group_by(CLUTCH_NUMBER) |> 
  summarise(AVG_EGG_SIZE = mean(EGG_SIZE)) |>
  ungroup()

clutch_data2 <- clutch_data |> 
  mutate(CLUTCH_NUMBER = as.factor(CLUTCH_NUMBER), 
         MALE = factor(MALE), 
         FEMALE = factor(FEMALE), 
         REGION = factor(REGION), 
         POPULATION = factor(POPULATION),
         CLUTCH_ORDER = factor(CLUTCH_ORDER),
         FEMALE_MASS = coalesce(FEMALE_MASS, MALE_MASS)) 

reprod.output <- clutch_data2 |> 
  inner_join(egg_size2, by="CLUTCH_NUMBER") |> 
  mutate(REPRODUCTIVE_OUTPUT = EGG_COUNT * AVG_EGG_SIZE)
```

# Exploratory data analysis 

## Reproductive output
```{r eda-1}
p1 <- ggplot(reprod.output, aes(x =REGION, y =REPRODUCTIVE_OUTPUT, fill =REGION)) + 
         geom_boxplot(color ="black") + 
         theme_classic()
``` 

```{r eda-2}
p2 <- ggplot(reprod.output, aes(x =REGION, y =REPRODUCTIVE_OUTPUT, fill =REGION, color =REGION)) + 
  geom_violin(alpha=.3, linewidth=1.5) + 
  geom_dotplot(binaxis = "y", stackdir = 'center') +
  theme_classic()
```

```{r eda-3}
p3 <- ggplot(reprod.output, aes(x =REPRODUCTIVE_OUTPUT, fill =REGION)) + 
  geom_dotplot(color ="black") + 
  geom_density(alpha=0.6) +
  theme_classic()
```

```{r eda-4}
p4 <- ggplot(clutch_data2, aes(x =REGION, y =FEMALE_MASS, fill =REGION, color =REGION)) + 
  geom_jitter(width=.05, size =3, alpha=.4) + 
  theme_classic()
```

```{r eda-summary}
ggarrange(p1,p2,p3,p4, 
          nrow = 2, 
          ncol =2)
``` 

# Fit model [random factors]

## Priors 

```{r piors}
reprod.output |> 
  group_by(REGION) |> 
  summarise(mean(REPRODUCTIVE_OUTPUT), 
            sd(REPRODUCTIVE_OUTPUT))

reprod.output.priors <- prior(normal(21, 2.5), class ="Intercept")
```

## Models {.tabset}

Hypothesis test will include:

0. Null model
1. EGG_COUNT ~ 1 + (1| FEMALE)
2. EGG_COUNT ~ 1 + (1| FEMALE) + (1| POPULATION)
3. EGG_COUNT ~ 1 + (1| FEMALE) + (1| CLUTCH_ORDER)
4. EGG_COUNT ~ 1 + (1| FEMALE) + (1| POPULATION) + (1| CLUTCH_ORDER)

### null
```{r model.null, cache=TRUE}
f.model.null <- bf(REPRODUCTIVE_OUTPUT ~ 1, 
                   family = gaussian())

model.null <- brm(f.model.null, 
                  data =reprod.output, 
                  prior =reprod.output.priors, 
                  warmup = 500, 
                  iter = 5000,
                  seed=123, 
                  cores=2, 
                  save_pars = save_pars(all=TRUE), 
                  sample_prior = "yes",
                  chains = 2, 
                  thin = 5, 
                  control = list(adapt_delta=0.95))
```

### model1 
```{r model1, cache=TRUE}
f.model1 <- bf(REPRODUCTIVE_OUTPUT ~ 1 + (1| FEMALE), 
                   family = gaussian())

model1 <- brm(f.model1, 
                  data =reprod.output, 
                  prior =reprod.output.priors, 
                  warmup = 500, 
                  iter = 5000,
                  seed=123, 
                  cores=2, 
                  save_pars = save_pars(all=TRUE), 
                  sample_prior = "yes",
                  chains = 2, 
                  thin = 5, 
                  control = list(adapt_delta=0.95))
``` 

### model2
```{r model2, cache=TRUE}
f.model2 <- bf(REPRODUCTIVE_OUTPUT ~ 1  + (1| FEMALE) + (1| POPULATION), 
                   family = gaussian())

model2 <- brm(f.model2, 
                  data =reprod.output, 
                  prior =reprod.output.priors, 
                  warmup = 500, 
                  iter = 5000,
                  seed=123, 
                  cores=2, 
                  save_pars = save_pars(all=TRUE), 
                  sample_prior = "yes",
                  chains = 2, 
                  thin = 5, 
                  control = list(adapt_delta=0.95))
``` 

### model3 
```{r model3, cache=TRUE}
f.model3 <- bf(REPRODUCTIVE_OUTPUT ~ 1 + (1| FEMALE) + (1| CLUTCH_ORDER), 
                   family = gaussian())

model3 <- brm(f.model3, 
                  data =reprod.output, 
                  prior =reprod.output.priors, 
                  warmup = 500, 
                  iter = 5000,
                  seed=123, 
                  cores=2, 
                  save_pars = save_pars(all=TRUE), 
                  sample_prior = "yes",
                  chains = 2, 
                  thin = 5, 
                  control = list(adapt_delta=0.95))
``` 

### model4 
```{r model4, cache=TRUE}
f.model4 <- bf(REPRODUCTIVE_OUTPUT ~ 1 + (1| FEMALE) + (1| POPULATION) + (1| CLUTCH_ORDER), 
                   family = gaussian())

model4 <- brm(f.model4, 
                  data =reprod.output, 
                  prior =reprod.output.priors, 
                  warmup = 500, 
                  iter = 5000,
                  seed=123, 
                  cores=2, 
                  save_pars = save_pars(all=TRUE), 
                  sample_prior = "yes",
                  chains = 2, 
                  thin = 5, 
                  control = list(adapt_delta=0.95))
```

### {-} 

## LOO 
```{r loo-comparison}
loo(model.null, model1, model2, model3, model4)
```

# fit model [fixed + random factors] {.tabset}

## priors 
```{r}
reprod.output |> 
  group_by(REGION) |> 
  summarise(mean(REPRODUCTIVE_OUTPUT), 
            sd(REPRODUCTIVE_OUTPUT))

reprod.output.priors <- prior(normal(21, 2.5), class ="Intercept") + 
  prior(normal(0, 3), class="b") + 
  prior(student_t(3, 0, 5.33), class="sigma")
```

## Model3.1 {.tabset}

### Model3.1
```{r model3.1, cache=TRUE}
f.model3.1 <- bf(REPRODUCTIVE_OUTPUT ~ 1 + REGION + 
                   scale(FEMALE_MASS, center=TRUE, scale=TRUE) + 
                   scale(DAYS_IN_TREATMENT, center=TRUE, scale=TRUE) + 
                   (1| FEMALE) + (1| CLUTCH_ORDER), 
                   family = gaussian())

model3.1 <- brm(f.model3.1, 
                  data =reprod.output, 
                  prior =reprod.output.priors, 
                  warmup = 500, 
                  iter = 5000,
                  seed=123, 
                  cores=2, 
                  save_pars = save_pars(all=TRUE), 
                  sample_prior = "yes",
                  chains = 2, 
                  thin = 10, 
                  control = list(adapt_delta=0.95))
saveRDS(model3.1, file="./09.Reproductive_output_files/model3.1.RDS")
```

### Model validation [DHARMa] 
```{r model3.1-validation}
pp_check(model3.1, type = 'dens_overlay_grouped', ndraws=150, group="REGION")

preds <- posterior_predict(model3.1, ndraws=250, summary=FALSE)
model3.1_resids <- createDHARMa(simulatedResponse = t(preds), 
                              observedResponse = reprod.output$REPRODUCTIVE_OUTPUT, 
                              fittedPredictedResponse = apply(preds, 2, median), 
                              integerResponse = 'student')
plot(model3.1_resids); testDispersion(model3.1_resids) 

model3.1 |> conditional_effects(spaghetti = TRUE, ndraws =200 )
```

### Model performance 

```{r model3.1-performance}
stan_trace(model3.1$fit) 
stan_ac(model3.1$fit) 
stan_rhat(model3.1$fit) 
stan_ess(model3.1$fit)
stan_dens(model3.1$fit, separate_chains = TRUE)
```

### {-} 

## Model3.1_gamma {.tabset}

### Model3.1_gamma 
```{r model3.1_gamma, cache=TRUE}
reprod.output.priors <- prior(normal(21, 2.5), class ="Intercept") + 
  prior(normal(0, 3), class="b")

f.model3.1_gamma <- bf(REPRODUCTIVE_OUTPUT ~ 1 + REGION + 
                   scale(FEMALE_MASS, center=TRUE, scale=TRUE) + 
                   scale(DAYS_IN_TREATMENT, center=TRUE, scale=TRUE) + 
                   (1| FEMALE) + (1| CLUTCH_ORDER), 
                   family = Gamma(link="log"))

model3.1_gamma <- brm(f.model3.1_gamma, 
                  data =reprod.output, 
                  prior =reprod.output.priors, 
                  warmup = 500, 
                  iter = 5000,
                  seed=123, 
                  cores=2, 
                  save_pars = save_pars(all=TRUE), 
                  sample_prior = "yes",
                  chains = 2, 
                  thin = 5, 
                  control = list(adapt_delta=0.95))
saveRDS(model3.1_gamma, file="./09.Reproductive_output_files/model3.1_gamma.RDS")
```

### Model validation [DHARMa] 
```{r model3.1_gamma-validation}
pp_check(model3.1_gamma, type = 'dens_overlay_grouped', ndraws=150, group="REGION")

preds <- posterior_predict(model3.1_gamma, ndraws=250, summary=FALSE)
model3.1_gamma_resids <- createDHARMa(simulatedResponse = t(preds), 
                              observedResponse = reprod.output$REPRODUCTIVE_OUTPUT, 
                              fittedPredictedResponse = apply(preds, 2, median), 
                              integerResponse = 'student')
plot(model3.1_gamma_resids); testDispersion(model3.1_gamma_resids) 

```

### {-}

## Model3.1_log

```{r model3.1_log, cache=TRUE}
f.model3.1_log <- bf(REPRODUCTIVE_OUTPUT ~ 1 + REGION + 
                   scale(FEMALE_MASS, center=TRUE, scale=TRUE) + 
                   scale(DAYS_IN_TREATMENT, center=TRUE, scale=TRUE) + 
                   (1| FEMALE) + (1| CLUTCH_ORDER), 
                   family = gaussian(link="log"))

model3.1_log <- brm(f.model3.1_log, 
                  data =reprod.output, 
                  prior =reprod.output.priors, 
                  warmup = 500, 
                  iter = 5000,
                  seed=123, 
                  cores=2, 
                  save_pars = save_pars(all=TRUE), 
                  sample_prior = "yes",
                  chains = 2, 
                  thin = 5, 
                  control = list(adapt_delta=0.95))
saveRDS(model3.1_log, file="./09.Reproductive_output_files/model3.1_log.RDS")
```

### Model validation [DHARMa] 
```{r model3.1_log-validation}
pp_check(model3.1_log, type = 'dens_overlay_grouped', ndraws=150, group="REGION")

preds <- posterior_predict(model3.1_log, ndraws=250, summary=FALSE)
model3.1_log_resids <- createDHARMa(simulatedResponse = t(preds), 
                              observedResponse = reprod.output$REPRODUCTIVE_OUTPUT, 
                              fittedPredictedResponse = apply(preds, 2, median), 
                              integerResponse = 'student')
plot(model3.1_log_resids); testDispersion(model3.1_log_resids) 

```

### {-} 

## {-}

# Partial plots 

```{r model3.1-partial plots }
model3.1 |> 
  conditional_effects(spaghetti = TRUE, ndraws=200)
```

# Model investigation {.tabset}

## summary 

```{r summar}
summary(model3.1) 
```

## ANOVA 

```{r Anova}
pes_posterior <- eta_squared_posterior(model3.1,
  ndraws = 500, # how many samples from the PPD?
  partial = TRUE, # partial eta squared
  # type 3 SS
  ss_function = car::Anova, type = 3,
  verbose = FALSE
) 

bayestestR::describe_posterior(pes_posterior, rope_ci=0.89)
```


## HDCI

```{r r-squared}
model3.1 |> bayes_R2(summary = FALSE) |> median_hdci(.width = 0.89)
```

## tidyMCMC 

```{r tidy}
tidyMCMC(model3.1, estimate.method='median', conf.int=TRUE, conf.method='HPDinterval', conf.level = 0.89)
```

## gather draws 

```{r gather_draws}
#model3.1 |> get_variables()
model3.1 |> gather_draws(`b_.*|sigma`, regex =TRUE) |> 
  median_hdci(.width=0.89)
``` 

## bayesplot 

```{r bayesplot-1}
model3.1 |> mcmc_plot(type='intervals')
```

## emmeans - pariwise 

```{r emmeans-pairwise}
model3.1 |> emmeans(pairwise ~ REGION, type="response") |> summary()

```

## probabilities 
```{r probabilities}
mtsqst <- model3.1 |> emmeans(pairwise ~ REGION)
mtsqrt2 <- mtsqst$contrasts |> gather_emmeans_draws()
mtsqrt2 %>% group_by(contrast) %>% dplyr::summarise(Prob = sum(.value>0)/n())
```
## {-} 

# Summary figure 
```{r summary-figure-1}
var <- get_variables(model3.1)
var1 <- get_variables(model3.1)[c(1:2)] 

int_draws_spread <- model3.1 |> spread_draws(!!!syms(var1)) 

int_draws_spread2 <- int_draws_spread |> 
  gather_draws(b_Intercept, b_REGIONleading) |> 
  left_join(int_draws_spread, by = c(".chain",".iteration",".draw"))


int_draws <- int_draws_spread2 |> 
  mutate(RCore = case_when(`.variable` == 'b_Intercept' ~ 
                             `.value`, 
                           `.variable` != 'b_Intercept' ~ 
                             `.value` + b_Intercept), 
         
         RLeading = case_when(`.variable` == 'b_Intercept' ~ 
                           `.value` + b_REGIONleading, 
                         `.variable` == 'b_REGIONleading' ~ 
                           `.value` + b_Intercept + `b_REGIONleading`))

int_draws_plotting <- int_draws |> 
  pivot_longer(cols = starts_with("R"), 
               names_to = "REGION", 
               values_to = "REPRODUCTIVE_OUTPUT") |> 
  transmute(LATITUDE = case_when(`.variable` == "b_Intercept" ~ "Low latitude", 
                                 `.variable` == "b_REGIONleading" ~ "High latitude"),
            REPRODUCTIVE_OUTPUT = REPRODUCTIVE_OUTPUT, 
            LATITUDE_B = LATITUDE,
            chain = `.chain`, 
            iteration = `.iteration`, 
            draw_n = `.draw`) 

reprod.output.plot <- int_draws_plotting |> 
  ggplot(aes(x=LATITUDE, y=REPRODUCTIVE_OUTPUT)) + 
  #geom_hline(yintercept = 0, linetype="dashed", linewidth=1, color="grey58", alpha=0.8) + 
  stat_halfeye(aes(fill = LATITUDE, fill_ramp = after_stat(level)), 
               point_interval = mode_hdci, 
               .width = c(.66, .89, .95)) + 
  scale_fill_ramp_discrete(na.translate=FALSE, 
                           labels =c("0.95","0.89","0.66"), 
                           name = "Credible interval") +
  scale_fill_manual(values = c("lightskyblue","coral"))+ 
  #scale_y_continuous(limits=c(0,2), breaks = seq(0,2, .5))+
  ylab("REPRODUCTIVE OUTPUT") + xlab("EXPERIMENTAL GROUP") +
  scale_x_discrete(labels = c("Low latitude" = paste0("Low latitude"), 
                              "High latitude" = paste0("High latitude"))) +
  #annotate("text", x=6.8,y=1.4, label = paste0(round(mean(growth3$MASS), 2)," (mm)"), color="grey58") +
  coord_flip() + 
  theme_classic() + 
  guides(fill = "none") + 
  theme(legend.position = c(.15,.86), 
        axis.title.y = element_text(margin = margin(r =0.3, unit = "in"), size = 12), 
        axis.title.x = element_text(margin = margin(t = 0.3, unit="in"), size =12), 
        legend.key = element_rect(color="black", size=1.25), 
        legend.background = element_rect(fill = alpha("blue", 0))); reprod.output.plot 
```