---
title: "11. rTPC"
author: "Elliott Schmidt"
date: "`r Sys.Date()`"
output: 
  html_document: 
    toc: true  
    toc_depth: 2
    toc_float: true
    code_folding: show
    collapse: no
    df_print: paged
    fig_caption: yes
    fig_height: 4
    fig_width: 6
    highlight: monochrome
    theme: cerulean
    latex_engine: xelatex
    keep_md: yes
---

# Scenario 

Within this chapter developmental plasticity was explored within _Acanthochromis polyacanthus_ that were collected from two different regions (i.e., low-latitude, Cairns, and high-latitude, Mackay). Fish were held in common garden experiments at 28.5 C. Clutch data was collected along with parental morphometeric data to determine how fish from each population performed at 28.5 C, a temperature that was shown to produce similar absoluate aerobic scope performances in a previous study [link]. Once hatched offspring were placed into three different temperature treatments, 28.5, 30, and 31.5 C. After approximately 5-6 months offspring length and weight was measured, as well as CTmax and respiration during CTmax trials. 

# Load packages 

```{r load-packages-1, warning=FALSE, message=FALSE}
library(tidyverse) # data manipulation
library(broom)
library(rTPC)
library(nls.multstart) 
library(patchwork)
```

# Set working directory 

```{r setwd-1, echo=FALSE}
knitr::opts_knit$set(root.dir="C:/Users/jc527762/OneDrive - James Cook University/PhD dissertation/Data/Chapter4_Latitude")
``` 

```{r setwd-2, echo=TRUE, eval=FALSE}
knitr::opts_knit$set(root.dir=working.dir)
```

# Import data 

This data set has no point outliers however, in the next chunk 3 samples will be 
discarded due to poor data quailty 

```{r import-data-1, message=FALSE}
lat_resp_dat <- read_delim("C:/Users/jc527762/OneDrive - James Cook University/PhD dissertation/Data/Chapter4_Latitude/import_files/lat_resp_dat_no_outliers.txt", 
    delim = "\t", escape_double = FALSE, 
    col_types = cols(area = col_skip(), rate.a.spec = col_skip()), 
    trim_ws = TRUE)
```

# Data manipulation 

```{r data-manipulation-1}
rows_of_data <- count(lat_resp_dat, sampleID)
lat_resp_dat2 <- lat_resp_dat |> 
  mutate(dev.temp = as.factor(dev.temp), 
         replicate = str_sub(sampleID, -1,-1), 
         population = factor(population)) |>
                                           # number of observations = 5758
  filter(sampleID != "56.CARL.137.28,5.1", # 5777 - 76 = 5682
         sampleID != "56.CARL.137.28,5.2", # 5701 - 64 = 5618
         sampleID != "60.LCKM.152.30.1"  # 5637 - 76 = 5542
  ) |> 
  filter(time_lag_sec >2001) |> # remove samples from first 5 cycles (i.e., first 33 minutes) 
  group_by(sampleID) |> 
  mutate(max_value_index = which.max(rate.output), 
         row_number = row_number(), 
         max.rate = max(rate.output), 
         low.rate = mean(rate.output[order(rate.output)[1:10]]), 
         net.rate = max.rate - low.rate) |> 
  #filter(row_number <= max_value_index) |>
  ungroup() |> 
  mutate(region = factor(region), 
         dev.temp =factor(dev.temp), 
         level = as.factor(case_when(tank >= 1 & tank <= 199 ~ 1,
                           tank >= 200 & tank <= 299 ~ 2,
                           tank >= 300 & tank <= 399 ~ 3,
                           TRUE ~ NA_real_)), 
         female = factor(female)) |> 
  unite("dev.temp.region",c(dev.temp,region), remove=FALSE) |> 
  mutate(dev.temp.region = factor(dev.temp.region)) |> 
  mutate(dev.temp.region =as.numeric(dev.temp.region)) 

lat_resp_dat2_extended <- lat_resp_dat2 |> 
  group_by(sampleID) |> 
  summarise(t =last(t)+0.1, 
            rate.output =0, 
            .groups ="drop") %>% 
  bind_rows(lat_resp_dat2, .) |> 
  arrange(sampleID, t)


```

# rTPC 

```{r echo=FALSE, eval=FALSE}
nls_multstart_progress <- function(formula, data = parent.frame(), iter, start_lower, 
                                   start_upper, supp_errors = c("Y", "N"), convergence_count = 100, 
                                   control, modelweights, ...){
  if(!is.null(pb)){
    pb$tick()
  }
  nls_multstart(formula = formula, data = data, iter = iter, start_lower = start_lower, 
                start_upper = start_upper, supp_errors = supp_errors, convergence_count = convergence_count, 
                control = control, modelweights = modelweights, ...)
}

# start progress bar and estimate time it will take
number_of_models <- 2
number_of_curves <- length(unique(lat_resp_dat2$sampleID))

# setup progress bar
pb <- progress::progress_bar$new(total = number_of_curves*number_of_models,
                                 clear = FALSE,
                                 format ="[:bar] :percent :elapsedfull")
```

**rTPC** is made to work across multiple data samples, however, we will first start by working with just one sample, fitting just one type of curve. The first curves that we are going to fit are called _sharpeschoolhigh_1981_ and _gaussian_1987_. 

## Sharpeschoolhigh_1981

```{r}
lat_resp_dat3 <- lat_resp_dat2 |> filter(sampleID =="101.LSBI.135.30.1")
start_vals <- get_start_vals(lat_resp_dat3$t, lat_resp_dat3$rate.output, model_name ='sharpeschoolhigh_1981')

mod <- nls.multstart::nls_multstart(rate.output~sharpeschoolhigh_1981(temp = t, r_tref, e, eh, th, tref = 35), 
                                    data=lat_resp_dat3, 
                                    iter=c(3,3,3,3), 
                                    start_lower =start_vals - 1, 
                                    start_upper =start_vals +1, 
                                    lower =get_lower_lims(lat_resp_dat3$t, lat_resp_dat3$rate.output, model_name ='sharpeschoolhigh_1981'), 
                                    upper =get_upper_lims(lat_resp_dat3$t, lat_resp_dat3$rate.output, model_name ='sharpeschoolhigh_1981'), 
                                    supp_errors='Y', 
                                    convergence_count =FALSE) 

summary(mod) 
preds <- data.frame(t =seq(min(lat_resp_dat3$t), max(lat_resp_dat3$t), length =100))
preds <- broom.mixed::augment(mod,newdata =preds)
x <- predict(mod, newdata =preds)
ggplot(preds) +
geom_point(aes(t, rate.output), lat_resp_dat3) +
geom_line(aes(t, .fitted), col = 'blue') +
theme_bw()
```

## Gaussian_1987

```{r}
start_vals <- get_start_vals(lat_resp_dat3$t, lat_resp_dat3$rate.output, model_name ='gaussian_1987')
mod <- nls.multstart::nls_multstart(rate.output~gaussian_1987(temp = t, rmax, topt, a), 
                                    data=lat_resp_dat3, 
                                    iter=c(3,3,3), 
                                    start_lower =start_vals - 1, 
                                    start_upper =start_vals +1, 
                                    lower =get_lower_lims(lat_resp_dat3$t, lat_resp_dat3$rate.output, model_name ='gaussian_1987'), 
                                    upper =get_upper_lims(lat_resp_dat3$t, lat_resp_dat3$rate.output, model_name ='gaussian_1987'), 
                                    supp_errors='Y', 
                                    convergence_count =FALSE) 

preds <- data.frame(t =seq(min(lat_resp_dat3$t), max(lat_resp_dat3$t), length =100))
preds <- broom.mixed::augment(mod,newdata =preds)
x <- predict(mod, newdata =preds)
ggplot(preds) +
geom_point(aes(t, rate.output), lat_resp_dat3) +
geom_line(aes(t, .fitted), col = 'blue') +
theme_bw()
```

We can can now see both curves fit to the data we have and how they fit differently. To make comparisons of curves easier we can fit multiple curves onto the same plot. Let's try some more curves and fit them onto the same plot. 

```{r }
lat_resp_dat3 <- lat_resp_dat2 |> filter(sampleID =="101.LSBI.135.30.1", 
                                         t >34) |> 
  select(sampleID, t, rate.output)

d_fits <- lat_resp_dat3 |> 
  #group_by(sampleID) |> 
  nest(data=c(t, rate.output)) |>
  mutate(
    gaussian =map(data, ~nls.multstart::nls_multstart(
      rate.output~gaussian_1987(temp = t, rmax, topt, a), 
                                    data=.x, 
                                    iter=c(3,3,3), 
                                    start_lower =get_start_vals(lat_resp_dat3$t, lat_resp_dat3$rate.output, model_name ='gaussian_1987') - 1, 
                                    start_upper =get_start_vals(lat_resp_dat3$t, lat_resp_dat3$rate.output, model_name ='gaussian_1987') +1, 
                                    lower =get_lower_lims(.x$t, .x$rate.output, model_name ='gaussian_1987'), 
                                    upper =get_upper_lims(.x$t, .x$rate.output, model_name ='gaussian_1987'), 
                                    supp_errors='Y', 
                                    convergence_count =FALSE)), 
    sharpeschoolhigh =map(data, ~nls.multstart::nls_multstart(rate.output~sharpeschoolhigh_1981(temp = t, r_tref, e, eh, th, tref = 30), 
                                    data=lat_resp_dat3, 
                                    iter=c(3,3,3,3), 
                                    start_lower =get_start_vals(lat_resp_dat3$t, lat_resp_dat3$rate.output, model_name ='sharpeschoolhigh_1981') - 1, 
                                    start_upper =get_start_vals(lat_resp_dat3$t, lat_resp_dat3$rate.output, model_name ='sharpeschoolhigh_1981') +1, 
                                    lower =get_lower_lims(lat_resp_dat3$t, lat_resp_dat3$rate.output, model_name ='sharpeschoolhigh_1981'), 
                                    upper =get_upper_lims(lat_resp_dat3$t, lat_resp_dat3$rate.output, model_name ='sharpeschoolhigh_1981'), 
                                    supp_errors='Y', 
                                    convergence_count =FALSE)), 
    weibull = map(data, ~nls_multstart(rate.output~weibull_1995(temp = t, a,topt,b,c),
                        data = lat_resp_dat3,
                        iter = c(4,4,4,4),
                        start_lower = get_start_vals(lat_resp_dat3$t, lat_resp_dat3$rate.output, model_name = 'weibull_1995') - 1,
                        start_upper = get_start_vals(lat_resp_dat3$t, lat_resp_dat3$rate.output, model_name = 'weibull_1995') + 1,
                        lower = get_lower_lims(lat_resp_dat3$t, lat_resp_dat3$rate.output, model_name = 'weibull_1995'),
                        upper = get_upper_lims(lat_resp_dat3$t, lat_resp_dat3$rate.output, model_name = 'weibull_1995'),
                        supp_errors = 'Y',
                        convergence_count = FALSE)), 
    pawar = map(data, ~nls_multstart(rate.output~pawar_2018(temp = t, r_tref, e, eh, topt, tref = 15),
                        data = lat_resp_dat3,
                        iter = c(4,4,4,4),
                        start_lower = get_start_vals(lat_resp_dat3$t, lat_resp_dat3$rate.output, model_name = 'pawar_2018') - 10,
                        start_upper = get_start_vals(lat_resp_dat3$t, lat_resp_dat3$rate.output, model_name = 'pawar_2018') + 10,
                        lower = get_lower_lims(lat_resp_dat3$t, lat_resp_dat3$rate.output, model_name = 'pawar_2018'),
                        upper = get_upper_lims(lat_resp_dat3$t, lat_resp_dat3$rate.output, model_name = 'pawar_2018'),
                        supp_errors = 'Y',
                        convergence_count = FALSE)),
    ratkowsky = map(data, ~nls_multstart(rate.output~ratkowsky_1983(temp = t, tmin, tmax, a, b),
                        data = lat_resp_dat3,
                        iter = c(4,4,4,4),
                        start_lower = get_start_vals(lat_resp_dat3$t, lat_resp_dat3$rate.output, model_name = 'ratkowsky_1983') - 10,
                        start_upper = get_start_vals(lat_resp_dat3$t, lat_resp_dat3$rate.output, model_name = 'ratkowsky_1983') + 10,
                        lower = get_lower_lims(lat_resp_dat3$t, lat_resp_dat3$rate.output, model_name = 'ratkowsky_1983'),
                        upper = get_upper_lims(lat_resp_dat3$t, lat_resp_dat3$rate.output, model_name = 'ratkowsky_1983'),
                        supp_errors = 'Y',
                        convergence_count = FALSE)),
    johnson_lewin = map(data, ~suppressWarnings(nls_multstart(rate.output~ johnsonlewin_1946(temp = t, r0, e, eh, topt),
                        data = lat_resp_dat3,
                        iter = c(4,4,4,4),
                        start_lower = get_start_vals(lat_resp_dat3$t, lat_resp_dat3$rate.output, model_name = 'johnsonlewin_1946') - 1,
                        start_upper = get_start_vals(lat_resp_dat3$t, lat_resp_dat3$rate.output, model_name = 'johnsonlewin_1946') + 1,
                        lower = get_lower_lims(lat_resp_dat3$t, lat_resp_dat3$rate.output, model_name = 'johnsonlewin_1946'),
                        upper = get_upper_lims(lat_resp_dat3$t, lat_resp_dat3$rate.output, model_name = 'johnsonlewin_1946'),
                        supp_errors = 'Y',
                        convergence_count = FALSE))))

d_stack <- select(d_fits, -data) %>% 
  pivot_longer(.,names_to = 'model_name', values_to ='fit', gaussian:ratkowsky)

newdata <- tibble(t =seq(min(lat_resp_dat3$t), max(lat_resp_dat3$t), length.out =100)) 
d_preds <- d_stack %>% 
  mutate(., preds =map(fit, augment, newdata =newdata)) |> 
  select(-fit) |> 
  unnest(preds) 

partial_data <- ggplot(d_preds, aes(t, .fitted)) +
  geom_line(aes(col =model_name), linewidth =1) +
  geom_point(aes(t, rate.output), 
             data =lat_resp_dat3) +
  theme_bw() + 
  theme(legend.position = "bottom"); partial_data


```

Fantastic! Now lets try to add in another sample so we can see how the different data curves fit on more than one sample. 

```{r}
lat_resp_dat3 <- lat_resp_dat2 |> filter(sampleID =="101.LSBI.135.30.1") |> 
  select(sampleID, t, rate.output)

d_fits <- lat_resp_dat3 |> 
  #group_by(sampleID) |> 
  nest(data=c(t, rate.output)) |>
  mutate(
    gaussian =map(data, ~nls.multstart::nls_multstart(
      rate.output~gaussian_1987(temp = t, rmax, topt, a), 
                                    data=.x, 
                                    iter=c(3,3,3), 
                                    start_lower =get_start_vals(lat_resp_dat3$t, lat_resp_dat3$rate.output, model_name ='gaussian_1987') - 1, 
                                    start_upper =get_start_vals(lat_resp_dat3$t, lat_resp_dat3$rate.output, model_name ='gaussian_1987') +1, 
                                    lower =get_lower_lims(.x$t, .x$rate.output, model_name ='gaussian_1987'), 
                                    upper =get_upper_lims(.x$t, .x$rate.output, model_name ='gaussian_1987'), 
                                    supp_errors='Y', 
                                    convergence_count =FALSE)), 
    sharpeschoolhigh =map(data, ~nls.multstart::nls_multstart(rate.output~sharpeschoolhigh_1981(temp = t, r_tref, e, eh, th, tref = 30), 
                                    data=lat_resp_dat3, 
                                    iter=c(3,3,3,3), 
                                    start_lower =get_start_vals(lat_resp_dat3$t, lat_resp_dat3$rate.output, model_name ='sharpeschoolhigh_1981') - 1, 
                                    start_upper =get_start_vals(lat_resp_dat3$t, lat_resp_dat3$rate.output, model_name ='sharpeschoolhigh_1981') +1, 
                                    lower =get_lower_lims(lat_resp_dat3$t, lat_resp_dat3$rate.output, model_name ='sharpeschoolhigh_1981'), 
                                    upper =get_upper_lims(lat_resp_dat3$t, lat_resp_dat3$rate.output, model_name ='sharpeschoolhigh_1981'), 
                                    supp_errors='Y', 
                                    convergence_count =FALSE)), 
    weibull = map(data, ~nls_multstart(rate.output~weibull_1995(temp = t, a,topt,b,c),
                        data = lat_resp_dat3,
                        iter = c(4,4,4,4),
                        start_lower = get_start_vals(lat_resp_dat3$t, lat_resp_dat3$rate.output, model_name = 'weibull_1995') - 1,
                        start_upper = get_start_vals(lat_resp_dat3$t, lat_resp_dat3$rate.output, model_name = 'weibull_1995') + 1,
                        lower = get_lower_lims(lat_resp_dat3$t, lat_resp_dat3$rate.output, model_name = 'weibull_1995'),
                        upper = get_upper_lims(lat_resp_dat3$t, lat_resp_dat3$rate.output, model_name = 'weibull_1995'),
                        supp_errors = 'Y',
                        convergence_count = FALSE)), 
    pawar = map(data, ~nls_multstart(rate.output~pawar_2018(temp = t, r_tref, e, eh, topt, tref = 15),
                        data = lat_resp_dat3,
                        iter = c(4,4,4,4),
                        start_lower = get_start_vals(lat_resp_dat3$t, lat_resp_dat3$rate.output, model_name = 'pawar_2018') - 10,
                        start_upper = get_start_vals(lat_resp_dat3$t, lat_resp_dat3$rate.output, model_name = 'pawar_2018') + 10,
                        lower = get_lower_lims(lat_resp_dat3$t, lat_resp_dat3$rate.output, model_name = 'pawar_2018'),
                        upper = get_upper_lims(lat_resp_dat3$t, lat_resp_dat3$rate.output, model_name = 'pawar_2018'),
                        supp_errors = 'Y',
                        convergence_count = FALSE)),
    ratkowsky = map(data, ~nls_multstart(rate.output~ratkowsky_1983(temp = t, tmin, tmax, a, b),
                        data = lat_resp_dat3,
                        iter = c(4,4,4,4),
                        start_lower = get_start_vals(lat_resp_dat3$t, lat_resp_dat3$rate.output, model_name = 'ratkowsky_1983') - 10,
                        start_upper = get_start_vals(lat_resp_dat3$t, lat_resp_dat3$rate.output, model_name = 'ratkowsky_1983') + 10,
                        lower = get_lower_lims(lat_resp_dat3$t, lat_resp_dat3$rate.output, model_name = 'ratkowsky_1983'),
                        upper = get_upper_lims(lat_resp_dat3$t, lat_resp_dat3$rate.output, model_name = 'ratkowsky_1983'),
                        supp_errors = 'Y',
                        convergence_count = FALSE)),
    johnson_lewin = map(data, ~suppressWarnings(nls_multstart(rate.output~ johnsonlewin_1946(temp = t, r0, e, eh, topt),
                        data = lat_resp_dat3,
                        iter = c(4,4,4,4),
                        start_lower = get_start_vals(lat_resp_dat3$t, lat_resp_dat3$rate.output, model_name = 'johnsonlewin_1946') - 1,
                        start_upper = get_start_vals(lat_resp_dat3$t, lat_resp_dat3$rate.output, model_name = 'johnsonlewin_1946') + 1,
                        lower = get_lower_lims(lat_resp_dat3$t, lat_resp_dat3$rate.output, model_name = 'johnsonlewin_1946'),
                        upper = get_upper_lims(lat_resp_dat3$t, lat_resp_dat3$rate.output, model_name = 'johnsonlewin_1946'),
                        supp_errors = 'Y',
                        convergence_count = FALSE))))

d_stack <- select(d_fits, -data) %>% 
  pivot_longer(.,names_to = 'model_name', values_to ='fit', gaussian:ratkowsky)

newdata <- tibble(t =seq(min(lat_resp_dat3$t), max(lat_resp_dat3$t), length.out =100)) 
d_preds <- d_stack %>% 
  mutate(., preds =map(fit, augment, newdata =newdata)) |> 
  select(-fit) |> 
  unnest(preds) 

all_data <- ggplot(d_preds, aes(t, .fitted)) +
  geom_line(aes(col =model_name), linewidth =1) +
  geom_point(aes(t, rate.output), 
             data =lat_resp_dat3) +
  theme_bw() + 
  theme(legend.position = "bottom")
```

```{r}
p = all_data + partial_data
p 
#ggsave("figures/rTPC_fitting_multiple_models.pdf", dpi =300, width =6, height=5, units ="in")
```

In the plots above it looks like the _ratkowsky_1983_ model fits the best. A typical ratkowsky fit is shown below.


```{r}
temps <- seq(20, max(lat_resp_dat3$t), length.out = 100)
preds <- ratkowsky_1983(temp = temps, tmin = 20, tmax = 37.5, a = 1, b =1); plot(temps, preds, type = "l")
```

Let's fit the _ratkowsky_1983_ model to some of our sample data. 

```{r}
lat_resp_dat3 <- lat_resp_dat2 |> filter(sampleID =="101.LSBI.135.30.1", t >35) |> 
  select(sampleID, t, rate.output)
mod <- nls.multstart::nls_multstart(rate.output~ratkowsky_1983(temp = t, tmin, tmax, a, b),
                        data = lat_resp_dat3,
                        iter = c(5,5,5,5),
                        start_lower = get_start_vals(lat_resp_dat3$t, lat_resp_dat3$rate.output, model_name = 'ratkowsky_1983') - c(1,0,0,-0.9),
                        start_upper = get_start_vals(lat_resp_dat3$t, lat_resp_dat3$rate.output, model_name = 'ratkowsky_1983') + 1,
                        lower = get_lower_lims(lat_resp_dat3$t, lat_resp_dat3$rate.output, model_name = 'ratkowsky_1983'),
                        upper = get_upper_lims(lat_resp_dat3$t, lat_resp_dat3$rate.output, model_name = 'ratkowsky_1983'),
                        supp_errors = 'Y',
                        convergence_count = FALSE) 

preds <- data.frame(t =seq(min(lat_resp_dat3$t), max(lat_resp_dat3$t), length =100))
preds <- broom.mixed::augment(mod,newdata =preds)
x <- predict(mod, newdata =preds)

ggplot(preds) +
geom_point(aes(t, rate.output), lat_resp_dat3) +
geom_line(aes(t, .fitted), col = 'blue') +
theme_bw()
```


Looks pretty good! Let's try to fit the _ratkowsky_1983_ to all of our samples now.  


```{r warning =FALSE}
lat_resp_dat4 <- lat_resp_dat2_extended |> 
  filter(t >32) |> 
  select(sampleID, t, rate.output) 

d_fits <- lat_resp_dat4 |> 
  #group_by(sampleID) |> 
  nest(data=c(t, rate.output)) |>
  mutate(ratkowsky = map(data, ~nls_multstart(rate.output~ratkowsky_1983(temp = t, tmin, tmax, a, b),
                        data = .x,
                        iter = c(3,3,3,3),
                        start_lower = get_start_vals(.x$t, .x$rate.output, model_name = 'ratkowsky_1983') - 1,
                        start_upper = get_start_vals(.x$t, .x$rate.output, model_name = 'ratkowsky_1983') + 1,
                        lower = get_lower_lims(.x$t, .x$rate.output, model_name = 'ratkowsky_1983'),
                        upper = get_upper_lims(.x$t, .x$rate.output, model_name = 'ratkowsky_1983'),
                        supp_errors = 'Y',
                        convergence_count = FALSE)))

d_preds <- mutate(d_fits, new_data =map(data, ~tibble(t =seq(min(lat_resp_dat4$t), max(lat_resp_dat4$t), length =100)))) |> 
  select(-data) |> 
  pivot_longer(names_to = 'model_name', values_to = 'fit', c(ratkowsky)) |> 
  mutate(preds =map2(fit, new_data, ~augment(.x, newdata =.y))) |>
  select(sampleID, model_name, preds) |> 
  unnest(preds) 

glimpse(d_preds)

d_preds_trimmed <- d_preds |> 
  group_by(sampleID, model_name) |> 
  mutate(peak_index = which.min(.fitted)) |>
  mutate(row_number = row_number()) |>
  filter(row_number <= peak_index) |>
  select(-peak_index, -row_number) |>
  ungroup()

p <- ggplot(d_preds_trimmed) + 
  geom_point(aes(t, rate.output), lat_resp_dat4) + 
  geom_line(data =d_preds, aes(t, .fitted), col="salmon", linetype ="dashed", alpha=0.5) +
  geom_line(aes(t, .fitted, col ="red")) + 
  facet_wrap(~sampleID, ncol =6) + 
  theme_bw() + ylim(0,1500) +
  theme(legend.position ='none') +
  labs(x = 'Temperature (ºC)',
       y = 'Resting metabolilc rate',
       title = 'All fitted thermal performance curves') 

p
```

Great job! 

We can now extra different parameters for each one of our samples including estimates for trait max, CTmin, CTmax, Q10, thermal_safety_margins, thermal_tolerance, breadth, and skewness. 

```{r}
d_params <- pivot_longer(d_fits, names_to ='model_name', values_to ='fit', c(ratkowsky)) |> 
  mutate(params =map(fit, calc_params)) |> 
  select(sampleID, model_name, params) |> 
  unnest(params) 
glimpse(d_params)
```


For more that can be done, visit the website for [rTPC](https://padpadpadpad.github.io/rTPC/)
