---
title: "12.TDTmodel"
author: "Elliott Schmidt"
date: "`r Sys.Date()`"
output: 
  html_document: 
    toc: true  
    toc_depth: 2
    toc_float: true
    code_folding: show
    collapse: no
    df_print: paged
    fig_caption: yes
    fig_height: 4
    fig_width: 6
    highlight: monochrome
    theme: cerulean
    latex_engine: xelatex
---

# Load packages 

```{r load-packages-1, warning=FALSE, message=FALSE}

library(ggpubr) # figure arrangement 
library(brms) # Bayesian models
library(StanHeaders)# needed to run Bayesian models
library(rstan) # needed to run Bayesian models
library(standist) # needs to be installed 
library(bayesplot) # needed for MCMC diagnostics 
library(DHARMa) # model validation 
library(ggdist) # partial plots 
library(tidybayes) # partial plots 
library(broom.mixed) # model investigation
library(emmeans) # pairwise comparisons
library(rstanarm) # pairwise comparisons - need for emmeans 
library(ggpubr) # arranging figures 
library(mgcv) # GAM 
library(modelr) # plotting
library(segmented) # piece wise regression 
library(strucchange) #piece wise regression 
library(patchwork) # figure 
library(modelsummary)
library(tidyverse) # data manipulation
```

# Set working directory 

```{r setwd-1, echo=FALSE}
knitr::opts_knit$set(root.dir="C:/Users/jc527762/OneDrive - James Cook University/PhD dissertation/Data/Chapter4_Latitude")
``` 

```{r setwd-2, echo=TRUE, eval=FALSE}
knitr::opts_knit$set(root.dir=working.dir)
```

# Import data 

This data set has no point outliers however, in the next chunk 3 samples will be 
discarded due to poor data quailty 

```{r import-data-1, message=FALSE}
ctmax <- read_delim("import_files/CTmax_data.txt", 
    delim = "\t", escape_double = FALSE, 
    col_types = cols(LOE_MEAN_EAS = col_number(), 
        ...30 = col_skip(), ...31 = col_skip()), 
    trim_ws = TRUE)

clutch_data <- read_delim("./import_files/clutch_data_2022_2023.txt")|> 
  mutate(PROJECT_CODE = factor(PROJECT_CODE), 
         FEMALE = factor(FEMALE)) |>
  filter(PROJECT_CODE == "2"| 
         PROJECT_CODE == "3"|
         PROJECT_CODE == "6"|
         PROJECT_CODE == "7")

illing <- read_csv("C:/Users/jc527762/OneDrive - James Cook University/PhD dissertation/Data/Chapter4_Latitude/Thermal-tolerances/Illing_data/Experimental_Data_Illing_et_al_Critical_Thermal_Maxima_of_Early_Life_Stages_of_Tropical_Fishes.csv", 
    skip = 26)
```

# Data manipulation 

```{r data manipulation, warning=FALSE}
ctmax2 <- ctmax |> 
  mutate(EXP_TANK = factor(EXP_TANK), 
         TRAY_ORD = factor(TRAY_ORD), 
         TRAY_COL = factor(TRAY_COL)) |>
  mutate(EXP_TANK = case_when(EXP_TANK = is.na(EXP_TANK) ~ "999", 
                              TRUE ~ EXP_TANK), 
         TRAY_ORD = case_when(TRAY_ORD = is.na(TRAY_ORD) ~ "999", 
                              TRUE ~ TRAY_ORD), 
         TRAY_COL = case_when(TRAY_COL = is.na(TRAY_COL) ~ "black", 
                              TRUE ~ TRAY_COL)) |>
  mutate(CLUTCH_NUMBER = factor(CLUTCH_NUMBER), 
         MALE = factor(MALE), 
         FEMALE = factor(FEMALE), 
         REGION = factor(REGION), 
         POPULATION = factor(POPULATION), 
         DATE_OF_HATCH = as.Date(DATE_OF_HATCH, format = "%d/%m/%Y"),
         DATE_CTMAX = as.Date(DATE_CTMAX, format = "%d/%m/%Y"),
         DEV_TEMP = factor(DEV_TEMP), 
         LEVEL = as.factor(case_when(TANK >= 1 & TANK <= 199 ~ 1,
                           TANK >= 200 & TANK <= 299 ~ 2,
                           TANK >= 300 & TANK <= 399 ~ 3,
                           TRUE ~ NA_real_)), 
          
         TANK = factor(TANK)) |> 
  left_join(distinct(dplyr::select(clutch_data, c("CLUTCH_NUMBER", "FEMALE","FEMALE_LAT","CLUTCH_ORDER")), FEMALE, .keep_all = TRUE), by="FEMALE") |> 
  mutate(CLUTCH_ORDER = factor(CLUTCH_ORDER)) |>
  filter(LOE_MEAN_EAS >= 35) |> 
  drop_na(FEMALE) |> 
  drop_na(POPULATION) |> 
  drop_na(TANK) |> 
  drop_na(LEVEL) |> 
  drop_na(CLUTCH_ORDER) |> 
  drop_na(EXPERIMENT) |> 
  drop_na(TRAY_COL) |> 
  drop_na(TRAY_ORD)  
  #mutate(time = as.numeric(difftime(LOE_TIME, RAMP_START_TIME, unit ="mins"))) |> 
  #drop_na(time)
```

## export data 

```{r}
dynamic_input <- ctmax2 |> 
  unite("group", REGION, DEV_TEMP, sep ="_") |>
  mutate(RAMP_RATE =0.1666667) |>
  dplyr::select(group, RAMP_RATE, LOE_MEAN_EAS) |> 
  rename(ramprate =RAMP_RATE, 
         dCTmax =LOE_MEAN_EAS)

write.csv(dynamic_input, "thermal-tolerances/dynamic_input.csv", row.names = FALSE)
```

## zvalues

```{r}
illing2 <- illing |> 
  filter(Species =="A.poly", 
         Treatment ==28,
         Rate !="Control") |> 
  mutate(Trial_time_m =Trial_time_h*60, 
         Trial_time_m_log10 =log10(Trial_time_m),
         Time_to_failure = (CTmax - 28.5)/as.numeric(Rate))  |> 
  mutate(Rate_min =as.numeric(Rate)/60)

zmodel28 <- lm(CTmax~log(Rate_min), illing2)
summary(zmodel28)

ggplot(data =illing2, aes(x=Rate_min, y=CTmax)) + 
  geom_point() + 
  geom_smooth(method ="glm", formula =y~log(x), 
              method.args = list(family = gaussian(link = 'log'))) + 
  theme_classic() + 
  ggtitle("z =0.89470")
```

```{r}

illing3 <- illing |> 
  filter(Species =="A.poly", 
         Treatment ==30,
         Rate !="Control")  |> 
  mutate(Trial_time_m =Trial_time_h*60, 
         Trial_time_m_log10 =log10(Trial_time_m),
         Time_to_failure = (CTmax - 30)/as.numeric(Rate))|> 
  mutate(Rate_min =as.numeric(Rate)/60)

zmodel30 <- lm(CTmax~log(Rate_min), illing3)
summary(zmodel30)

ggplot(data =illing3, aes(x=Rate_min, y=CTmax)) + 
  geom_point() + 
  geom_smooth(method ="glm", formula =y~log(x), 
              method.args = list(family = gaussian(link = 'log'))) + 
  theme_classic() + 
  ggtitle("z =0.86739")
```

Use the calculated z-value to run TFT_from_Dynamic.R script as provided by Orsted et al., 2022. Then import necessary data files.

Using R value for 30C trials from Illing et al., 2020, because CTmax trials started at 30C and this was the mean developmental temperature. 

```{r}
extra_sCTmax <- read_csv("Thermal-tolerances/outputs/extra_sCTmax.csv", 
     col_types = cols(extra_t_coma_pred = col_number())) 

sCTmax_t_coma <- read_csv("Thermal-tolerances/outputs/sCTmax_t_coma.csv", 
    col_types = cols(...1 = col_skip(), t_coma = col_factor(levels = c("60", 
        "1140", "10080", "20160")), sCTmax_pred = col_number(), 
        z_pred = col_number()))
```

# Data exploration 
```{r}
ggplot(extra_sCTmax, aes(x=extra_sCTmax, y =(extra_t_coma_pred/60)/24, color =group)) + 
  geom_hline(yintercept = 1, linetype ="dashed", color ="grey1") +
  geom_hline(yintercept = 7, linetype ="dashed", color ="grey38") +
  geom_hline(yintercept = 14, linetype ="dashed", color ="grey75") +
  geom_point() + 
  geom_smooth(method ="glm", formula =y~log(x), 
              method.args = list(family = gaussian(link = 'log')), 
              se =FALSE) +
  scale_color_manual(values = c("coral", "red2","firebrick4","lightskyblue" ,"dodgerblue2", "dodgerblue4")) + 
  scale_y_continuous(breaks =seq(from =0, to =52, by =7)) +
  ylab("Time (days)") + xlab("Temperature \u00b0C") +

  theme_classic()


```

# Linear
```{r}
ggplot(extra_sCTmax, aes(x=extra_sCTmax, y =log10((extra_t_coma_pred/60)/24), color =group)) + 
  geom_point() + 
  geom_smooth(method ="lm", 
              se =FALSE) +
  scale_color_manual(values = c("coral", "red2","firebrick4","lightskyblue" ,"dodgerblue2", "dodgerblue4")) + 
  scale_y_continuous(breaks =seq(from =0, to =52, by =7)) +
  ylab("Time (days)") + xlab("Temperature \u00b0C") +
  theme_classic()

extra_sCTmax
```

```{r}
sCTmax_t_coma
```

